---
title: "Programming Exercises"
author: "Kejing Li"
output: github_document
---

## Load necessary libraries

```{r}
library(tidyverse)
```

## Compute the number of unique values in each column of `iris`

### Using a `for` loop

```{r}
#use `for` loop by coloum, store output in integer
unique <- vector("integer", ncol(iris))
for(i in seq_along(iris)){
#compute distinct values
  unique[[i]] <- n_distinct(iris[[i]])
#create named output
  names(unique) <- names(iris)
}
unique

```

### Using a `map` function

```{r}
iris %>%
#output is integer
  map_int(n_distinct)
```

## Calculate the square of each element in vector `x`

```{r}
x <- 1:30
x
```

### Using a `for` loop

```{r}
#output is double
square <- vector("double", length(x))
for(i in seq_along(x)){
  square[[i]] <- i^2
}
square
```

### Using a `map` function

```{r}
x %>%
#use shortcut for anonymous function
  map_dbl(~.x^2)
```

## Write a function to calculate length of sides in a right-triangle using the Pythagorean Theorem

```{r}
#test if input it's numeric and >0
valid_side <- function(x) {
  if (is.numeric(x) && x > 0) {
    return(TRUE)
  } 
  return(FALSE)
}

#three different input conditions  
pythagorean <- function(a = NA, b = NA, c = NA){
  if (is.na(a) && valid_side(b) && valid_side(c) && b < c){
    return(sqrt(c^2 - b^2))
  } else if (is.na(b) && valid_side(a) && valid_side(c) && a < c){
      return(sqrt(c^2 - a^2))
  } else if (is.na(c) && valid_side(a) && valid_side(b)){
      return(sqrt(a^2 + b^2))
  } else {
      stop("Please input only 2 valid numeric values(note that a<c and b<c)")
  }
}  
```

### test
pythagorean(a=1,b=2,c=3)
pythagorean(a=1)
pythagorean(a=1,b="1.2")
pythagorean(a=1,b="1.2",c=3)
pythagorean(a=1,b=2,c="na")
pythagorean(a=1,b=2,c=FALSE)
pythagorean(a=1,b=2)
pythagorean(a=1,c=1)
pythagorean(b=1,c=3)
pythagorean(a=2,c=3)
pythagorean(a=2,b=3)

## Session info

```{r}
devtools::session_info()
```


