---
title: "Exploring World Bank Data"
author: "Kejing Li"
output: github_document
---

## Load necessary libraries

```{r}
library(tidyverse)
```

## Introduction 

>“Gender inequality is not only a pressing moral and social issue, but also a critical economic >challenge.”     — McKinsey Global Institute

This report intends to explore the female representation in top management. 

Gender inequality is a commonplace talk of an old scholar. However, in recent years, the phenomenon is discussed under a new context - leadership in business. Incessant evidences suggest that the gender diversity contributes to the bussiness operation. To better understand the current development, this report analyzes four variables from the world bank database:

1. High-technology exports (% of manufactured exports)
1. Firms with female top manager (% of firms)
1. Firms with female participation in ownership (% of firms)
1. Start-up procedures to register a business 

## Write a function to import the data files

```{r}
read_and_tidy <- function(path) {
  data <- read.csv(path, skip = 4) %>%
 #select & filter data needed for analysis
  select(-Country.Code, -Indicator.Name)%>%
  filter(Indicator.Code %in% c("IC.FRM.FEMO.ZS",
                               "IC.FRM.FEMM.ZS",
                               "IC.REG.PROC.FE",
                               "TX.VAL.TECH.MF.ZS"))%>%
  #put each observations in row, each variables in its columns
    pivot_longer(-c("Country.Name",
                    "Indicator.Code"),
                 names_to = "Year",
                 values_to = "Value",
                 names_prefix = "X") %>%
    pivot_wider(names_from = "Indicator.Code",
                values_from = "Value") %>%
  #remane the code in to infomative names
    rename(hitech_export = TX.VAL.TECH.MF.ZS,
           female_register_procedure = IC.REG.PROC.FE,
           female_ownership_participation = IC.FRM.FEMO.ZS,
           female_top_management = IC.FRM.FEMM.ZS)
  return(data)     
}
```

## Import the data


```{r, warning=FALSE }
# silent the warning message
directory <- dir(path = "data_world_bank", full.names = TRUE)
#create an empty dataframe
data <- data.frame()
#use 'for' loop to input and combine data
for (i in seq_along(directory)){
  data <- bind_rows(data, read_and_tidy(directory[i]))
}

```

## Explore the data

### Firms with female participation in ownership by year

As shown below, the data start merely from the 21 century when the phenomenon came into the public attention. But the overall trend doesn't appear any upward nor downward trend over the period. Whatever the variation, less than half of the firms have female participated in the ownership.

```{r}
data %>%
  drop_na(female_ownership_participation)%>%
  ggplot()+
  geom_boxplot(aes(Year,female_ownership_participation))+
  labs(title = "Firms with female participation in ownership",
        x = "Year",
        y = "% of firms")
```


###  Firms with female top manager by year

As like the female participation in ownership data, percentage of firms with female manager don't have apparent trend over the years concerned, but with a even lower average, fluctuating between 10% to 20%. Females are largely underrepresented in the top management.

```{r}
data %>%
  drop_na(female_top_management)%>%
  group_by(Year) %>%
  summarize(female_top_management = mean(female_top_management)) %>%
  ggplot()+
  geom_col(aes(Year, female_top_management))+
  labs(title = "Firms with female top manager",
        x = "Year",
        y = "% of firms")
```

### Covariance of female participation in ownership and female top manager

Since neither the percentage of female in top mangement nor female participation in ownership alone indicate any trend along the years. Doubts arise whether these two variables are telling the same story. Covariance analysis is hereby given that demonstrates these two variables are positively related to each other. Where females appear more often as top managers, female participation in ownership is correspondingly higher. This result suggests the position of female in leadership is consistent across different measurements.

```{r}
data%>%
  drop_na(female_ownership_participation, female_top_management) %>%
  group_by(Country.Name)%>%
  ggplot()+
  geom_smooth(aes(female_top_management,female_ownership_participation))+
labs(title = "Relationship between female participation in ownership and female top manager",
        x = "Female top manager(% of firms)",
        y = "Female participation in ownership")

```

### Look into the phenomenon

Previous analysis proved the existence of the gender inequality, and showed a stagnant situation. Such situation set me thinking, wondering what relates to or causes the phenomenon. Therefore, shown below, I tested two possible related variables, but the output failed to give any enlightment. However, it could be just that the number or quality of dataset isn't good enough to reflect the reality. Besides, other variables may be included to give more insights.  

#### Covariance of Start-up procedures to register a business(female) and female top manager


```{r}
data%>%
  drop_na(female_register_procedure, female_top_management) %>%
  group_by(Country.Name)%>%
  ggplot()+
  scale_x_continuous(limits = c(0, 15))+
  geom_boxplot(aes(female_register_procedure, female_top_management,
                  group = cut_width(female_register_procedure, 2)))+
  labs(title = "Relationship between  Start-up procedures to register a business(female) and female top manager",
        x = "Start-up procedures to register a business(female)",
        y = "Female top manager (% of firms)")
```

#### Covariance of High-technology exports and female top manager
```{r}
data%>%
  drop_na(hitech_export, female_top_management) %>%
  group_by(Country.Name)%>%
  ggplot(aes(hitech_export, female_top_management))+
  geom_point(alpha = 1/2)+
  geom_smooth()+
  labs(title = "Relationship between  High-technology exports and female top manager",
        x = "High-technology exports (% of manufactured exports)",
        y = "Female top manager (% of firms)")
```


## Session info

```{r}
devtools::session_info()
```


